% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.23609.03689}{}}%
Freudenthaler, H. H., Schrausser, D. G., Pfurtscheller, G., \& Neubauer,
A. C. 2000. {``{Gender differences in the relationship between
intelligence and cortical activation}.''} In \emph{{XXVII International
Congress of Psychology}}. Stockholm, Sweden.
\url{https://doi.org/10.13140/RG.2.2.23609.03689}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.21487.30885}{}}%
Neubauer, A. C., Fink, A., \& Schrausser, D. G. 2001. {``{Intelligence
and neural efficiency: The influence of task content and sex on brain-IQ
relationship}.''} In \emph{{Symposium 'Physiological approaches to human
intelligence' at the 10th Biennial Meeting of the International Society
for the Study of Individual Differences (ISSID)}}. Edinburgh, United
Kingdom: {The University of Edinburgh}.
\url{https://doi.org/doi.org/10.13140/RG.2.2.21487.30885}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.34909.08166}{}}%
Neubauer, A. C., Schrausser, D. G., \& Fink, A. 2001. {``{Intelligenz
und neurale Effizienz gemessen mittels EEG-Kohärenz}.''} In \emph{{6.
Arbeitstagung der Fachgruppe Differentielle Psychologie,
Persönlichkeitspsychologie \& Psychologische Diagnostik}}. Leipzig,
Deutschland: {Universität Leipzig}.
\url{https://doi.org/10.13140/RG.2.2.34909.08166}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.16108.64640ux2f1}{}}%
Neubauer, A. C., Schrausser, D. G., \& Freudenthaler, H. H. 2000.
{``{Psychometrische Intelligenz und kortikale Aktivierung bei der
Bearbeitung kognitiver Aufgaben}.''} In \emph{{42. Kongreß der Deutschen
Gesellschaft für Psychologie}}. Jena, Deutschland:
{Friedrich-Schiller-Universität Jena}.
\url{https://doi.org/10.13140/RG.2.2.16108.64640/1}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.13162.59847}{}}%
Neubauer, A. C., Schrausser, D. G., Sange, G., Pfurtscheller, G. 1999.
{``{Psychometrische Intelligenz und kortikale Aktivierung bei der
Bearbeitung elementar-kognitiver Aufgaben}.''} In \emph{{5.
Arbeitstagung der Fachgruppe Differentielle Psychologie,
Persönlichkeitspsychologie \& Psychologische Diagnostik}}. Wuppertal,
Deutschland: {Bergische Universität Wuppertal}.
\url{https://doi.org/10.13140/RG.2.2.13162.59847}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.19532.69768}{}}%
Schrausser, D. G. 1998. {``{Die Permutationsmethode: Voraussetzungsfrei
testen}.''} In \emph{{41. Kongreß der Deutschen Gesellschaft für
Psychologie}}. Dresden, Deutschland: {Technische Universität Dresden}.
\url{https://doi.org/10.13140/RG.2.2.19532.69768}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.33203.50721}{}}%
---------. 1999. {``{Konstruktion einer Skala zur Erfassung
selbstwahrgenommener Leistungsfähigkeit in 3 Inhaltsklassen
Psychometrischer Intelligenz}.''} In \emph{{5. Arbeitstagung der
Fachgruppe Differentielle Psychologie, Persönlichkeitspsychologie \&
Psychologische Diagnostik}}. Wuppertal, Deutschland: {Bergische
Universität Wuppertal}.
\url{https://doi.org/10.13140/RG.2.2.33203.50721}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.14805.91369}{}}%
---------. 2002. {``{Exakte Verfahren oder Asymptotische
Approximation?}''} In \emph{{3. Tagung der österreichischen Gesellschaft
für Psychologie (ÖGP)}}. Salzburg, Österreich: {Universität Salzburg}.
\url{https://doi.org/10.13140/RG.2.2.14805.91369}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.24814.89929}{}}%
Schrausser, D. G., Fink, A., \& Neubauer, A. C. 2001. {``{Intelligence
and neural efficiency as determined by EEG-Coherence}.''} In
\emph{{Symposium 'Physiological approaches to human intelligence' at the
10th Biennial Meeting of the International Society for the Study of
Individual Differences (ISSID)}}. Edinburgh, United Kingdom: {The
University of Edinburgh}.
\url{https://doi.org/10.13140/RG.2.2.24814.89929}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.13962.13768}{}}%
---------. 2002. {``{Intelligenz und neurale Effizienz gemessen mittels
EEG-Kohärenz}.''} In \emph{{5. Tagung der Österreichischen Gesellschaft
für Psychologie (ÖGP)}}. Wien, Österreich: {Universität Wien}.
\url{https://doi.org/10.13140/RG.2.2.13962.13768}.

\end{CSLReferences}

\end{document}
