% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Schrausser94993376}{}}%
Scambor, C., \& Schrausser, D. G. 2023a. {``{Introduction (part II,
permutation tests for repeated measurement designs)}.''} \emph{Thesis
Chapters}. Academia. \url{https://www.academia.edu/94993376}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser94481830}{}}%
---------. 2023b. {``{Philosophy of science fundamentals}.''}
\emph{Thesis Chapters}. Academia.
\url{https://www.academia.edu/94481830}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser94482216}{}}%
---------. 2023c. {``{Statistical methods from the point of view of
philosophy of science}.''} \emph{Thesis Chapters}. Academia.
\url{https://www.academia.edu/94482216}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserThesis}{}}%
Schrausser, D. G. 1996a. {``{Permutationstests: Theoretische und
praktische Arbeitsweise von Permutationsverfahren beim unverbundenen 2
Stichprobenproblem}.''} Mag.rer.nat., Universität Graz:
Naturwissenschaftliche Fakultät.
\url{https://doi.org/10.13140/RG.2.2.24500.32640/1}.

\leavevmode\vadjust pre{\hypertarget{ref-SchrausserRG.2.2.10698.44482}{}}%
---------. 1996b. {``{Einführung in die Benutzung von SPSS}.''} In
\emph{Methoden Skriptum}, edited by ÖH. Österreichische
Hochschülerschaft, ÖH.
\url{https://doi.org/10.13140/RG.2.2.10698.44482}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser75975252}{}}%
---------. 1998. {``{Exakte Verfahren oder Asymptotische
Approximation?}''} In \emph{Perspektiven Psychologischer Forschung in
Österreich}, edited by Glück, J., Jirasco, M., \& Rollett, B. Vol. 2.
WUV-Univ.-Verl., Wien. \url{https://www.worldcat.org/de/title/75975252}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser82224369}{}}%
---------. 2022a. {``{Thesis chapter 1: Introduction}.''} \emph{Thesis
Chapters}. Academia. \url{https://www.academia.edu/82224369}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser96788147}{}}%
---------. 2022b. {``{Thesis chapter 2: Random selection as correlative
construct}.''} \emph{Thesis Chapters}. Academia.
\url{https://www.academia.edu/96788147}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser81286148}{}}%
---------. 2022c. {``{Thesis chapter 4: Permutation tests to reveal
interaction effects}.''} \emph{Thesis Chapters}. Academia.
\url{https://www.academia.edu/81286148}.

\leavevmode\vadjust pre{\hypertarget{ref-Schrausser82083349}{}}%
---------. 2022d. {``{Thesis: Summaries and Discussions}.''}
\emph{Thesis Chapters}. Academia.
\url{https://www.academia.edu/82083349}.

\end{CSLReferences}

\end{document}
